3D MAGNETIC MODELLING FOR ELIPSOIDS

### 2016-12-02 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Atualizacao da metodologia equacao superficie elipsoide

>>>>

The equation of the surface of an ellipsoid can be written in a matrix form as:
\begin{equation}
(\bar{\textbf{r}} - \bar{\textbf{r}}_c)^T \bar{\bar{A}} (\bar{\textbf{r}} - \bar{\textbf{r}}_c) = 1,
\end{equation}

and $\bar{\bar{A}}$ is a 3X3 matrix formed by:
\begin{equation}
\bar{\bar{A}} = \bar{\bar{V}} 
\left[\begin{matrix} 
\dfrac{1}{a^2+s} & 0 & 0 \\
0 & \dfrac{1}{b^2+s} & 0 \\
0 & 0 & \dfrac{1}{c^2+s}
\end{matrix}\right]
\bar{\bar{V}}^T,
\end{equation}

where the columns of $\bar{\bar{V}}$ are the eigenvectors that represents the principal axes of the ellipsoid and the diagonal of the middle matrix the eigenvalues that represents the reciprocals of the square of the semi-axes $a^{-2}$, $b^{-2}$ and $c^{-2}$.
